Note on Non-Detections Model

### 2012-04-09 tex/ms.tex
Added Nat's code (py/lomb_scargle_censor.py), my note from 20120221, and the current ms tex/pdf

\shorttitle{Fitting the undetected}
\shortauthors{}
\title{Fitting the undetected:  Light-curve feature estimation in the presence of carelessly reported non-detections}
\author{
Some wild \& crazy guys
}
%
%\altaffiltext{1}{Astronomy Department, University of California, Berkeley, CA, 94720-7450, USA}
%\altaffiltext{2}{Statistics Department, University of California, Berkeley, CA, 94720-7450, USA}
%\altaffiltext{*}{E-mail: {\tt jwrichar@stat.berkeley.edu}}

@@

\begin{abstract}
In multi-epoch imaging surveys, faint variable sources will not be
detectable at all epochs.  In principle, the best approach is to
perform photometric measurements anyway, so that there is a datum
required at at every epoch.  In practice, in most surveys we are
provided at some epochs only with upper limits; in some not even upper
limits but just the information that the star was not observed.  Here
we demonstrate with real data on periodic variables from the All-Sky
Automated Survey that these non-detections are nonetheless useful in
fitting and parameter estimation; their inclusion improves both
precision and accuracy.  One novel aspect of this work is that we do
not require the data source to include accurate---or even
any---information about the uncertainty variances on detections or the
values of the upper limits; we find that we can model these as latent
variables, even when they are different at every epoch.
\end{abstract}

@@

@@

A photometric survey (think of it as operating in a single photometric
bandpass for now) scans over the celestial position of a particular
variable star at a large number of times $t_i$.  At each of these
times, the imaging data are analyzed by (not awesome) software, which
treats each scan as a \emph{completely independent} survey.  That is,
when analyzing the data from time $t_i$, none of the information from
any of the other times is used in any way.

@@

>>>>

\shorttitle{Fitting the Undetected}
\shortauthors{}
\title{Fitting the Undetected:  Light-curve Feature Estimation in the Presence of Non-detections}
\author{
Some wild \& crazy guys
}
%
%\altaffiltext{1}{Astronomy Department, University of California, Berkeley, CA, 94720-7450, USA}
%\altaffiltext{2}{Statistics Department, University of California, Berkeley, CA, 94720-7450, USA}
%\altaffiltext{*}{E-mail: {\tt jwrichar@stat.berkeley.edu}}

@@

\begin{abstract}
In multi-epoch imaging surveys, faint variable sources will not be
detectable at all epochs.  In principle, the best approach is to
perform photometric measurements anyway, so that there is a datum
recorded at at every epoch.  In practice, most surveys only provide
detection upper limits at some epochs; in some not even upper
limits but just the information that the star was not observed.  Here
we demonstrate with real data on periodic variables from the All-Sky
Automated Survey (ASAS) that these non-detections are nonetheless useful in
fitting and parameter estimation; their inclusion improves both
precision and accuracy.  One novel aspect of this work is that we do
not require the data source to include accurate---or even
any---information about the uncertainty variances on detections or the
values of the upper limits; we find that we can model these as latent
variables, even when they are different at every epoch.  Using realistic
simulations of Mira variable stars, we obtain amplitude estimates that
are {\bf XXX\%} more accurate by incorporating the non-detections into
the analysis.  For  Mira and RR Lyrae variables observed by ASAS, our
method obtains a tighter period - amplitude relationship than the standard
technique.
\end{abstract}

@@

Surveys working in real-time tend to analyze each image with an eye to populating databases quickly. Unless a particular region of the sky gets special treatment (such as it is a known place of interest), discovery of variability happens by comparison of flux values at the database level. Analysis on such databases of transient/variables thus deals with censored data where there is often less information available that there should be. Even then, we might be able to infer what the thresholds were based on S/N measurements of objects neighboring the source of interest.

@@

A photometric survey (think of it as operating in a single photometric
bandpass for now) scans over the celestial position of a particular
variable star  a large number of times $t_i$.  At each of these
times, the imaging data are analyzed by software, which
treats each scan as a \emph{completely independent} survey.  That is,
when analyzing the data from time $t_i$, none of the information from
any of the other times is used in any way.

@@

\joey{let's make a point to stress variable discovery}

### 2012-04-09 tex/note_jwr_20120221.tex
Added Nat's code (py/lomb_scargle_censor.py), my note from 20120221, and the current ms tex/pdf

For each astronomical object, a photometric survey measures a multi-epoch light curve over $N$ (typically unevenly spaced) epochs.  At each epoch, $t_i$, the survey takes an exposure at the location of the object and either (a) detects the object and records an estimate of its photon flux, $\fobs$ and the statistical uncertainty in that estimate, $\sobs$, or (b) fails to detect the object in the presence of the noise from the sky and instrument.  In the latter case, most modern surveys either record a reference value to signify that no detection was made (as is done in ASAS) or an estimate of the upper detection limit, which is the brightest the object could have been given that it was not detected at a significant level by the software.

There are many reasons that a source might not show up in a catalog.  These include:
\begin{itemize}
\item low S/N of the source, due either to a higher noise level or a fainter signal,
\item the source falling outside of the detection window (e.g., near chip edge),
\item occulting of the source by an artifact of the detector (e.g., hot pixels, masked out), or
\item the source was out-shown by an intervening object (e.g., asteroid, comet, airplane, etc.).
\end{itemize}
Here, we present a statistical model that can be used to detect variable sources and model their variability using multi-epoch light curves containing epochs of non-detection.  Previous efforts to detect and model variability using multi-epoch photometry have ignored non-detections (REFs) or used them in an ad-hoc manner lacking statistical rigor (REFs).

In this paper, we will assume that $\fobs$ and $\sobs$ take on real-valued numbers in epochs for which the source was detected and receive the reference value {\tt NA} in epochs where no detection was made. For notational convenience we assemble all the light curve data into a data set $D$ given by
\begin{eqnarray}\displaystyle
D &\equiv& \{D_i\}
\\
D_i &\equiv& (\fobs, \sobs)
\quad ,
\end{eqnarray}
where $(\fobs, \sobs)$ are the light curve measurements  at $t_i$.  The goal, for each astronomical object, is to maximize the likelihood of the light curve data, $D$, given a set of model parameters that describe the variability of the object and the characteristics of the observations.

@@

To model the mean brightness of the light curve as a function of time, we use a multiple-harmonic Fourier model with oscillation frequency $\omega$,
\begin{eqnarray}\displaystyle
\mu_i &=& \sum_{k=1}^K A_k\, \sin (2 \pi t_i \omega  k + \phi_k)
\quad ,
\end{eqnarray}
where $A_k$ is the amplitude of the $k^{\rm th}$ harmonic of frequency $\omega$ and $\phi_k$ is the relative phase offset of harmonic $k$.  In this analysis, we will fix the number of harmonics to $K=3$, though in principle we can use the data to choose the appropriate $K$ to capture the complexity of the light curve.  In addition to this expected brightness, we assume that there is model uncertainty or stochastic variation, leading to a \emph{model variance} $s_\mu^2$ at each point (assumed constant but easily generalized).

Additionally, we need to instantiate a latent variable, $b_i$, to represent the detection limit, in units of flux, for epoch $i$.  The $b_i$ parameter is essential because it constrains the possible values of the mean brightness, $\mu_i$, of the light curve when there is a non-detection.  By employing a hierarchical model for the distribution of $b_i$, we can fully utilize all of the information encoded in both the detections and non-detections when computing the data likelihood.   At each epoch, we connect the observed flux, $\fobs$ to the observable flux of the object, $f_i$, via the detection limit, $b_i$ by
\begin{eqnarray}\displaystyle
\fobs &=& \left\{\begin{array}{ll}
  f_i & \mbox{if $f_i \ge b_i$} \\
  \texttt{NA} & \mbox{if $f_i < b_i$} \\
\end{array} \right.
\end{eqnarray}
so that the observed flux is \texttt{NA} only when the true observable flux, $f_i$, is below the detection limit, $b_i$.  And similarly,
\begin{eqnarray}\displaystyle
\sobs &=& \left\{\begin{array}{ll}
  s_i & \mbox{if $f_i \ge b_i$} \\
  \texttt{NA} & \mbox{if $f_i < b_i$} \\
\end{array} \right.
\end{eqnarray}
so that the true observable standard error of the flux measurement is \texttt{NA} only when the true observable flux is below the detection limit.

@@

Hence, our initial model consists of the parameter vectors $\{b_1,...,b_N\}$ and $\{\sigma_1,...,\sigma_N\}$, and the model parameters
\begin{eqnarray}\displaystyle
\theta &\equiv& (\omega, \{A_k\}, \{\phi_k\}, s_\mu^2) \quad ,
\end{eqnarray}
along with prior information about observation times, $\{t_1,...,t_N\}$ and other prior assumptions, which we make explicit by creating the prior information set
\begin{eqnarray}\displaystyle
I &\equiv& (\{t_i\}, \mbox{assumptions}) \quad .
\end{eqnarray}
Our goal is to write down the form of the likelihood of the data, $D$, given $\theta$ and $I$.  Then, for each light curve we can find the vector $\theta$ that maximizes the data likelihood.

@@

We model the observed flux, $\fobs$, as a Gaussian distribution with variance that has both measurement ($\sigma_i$) and model ($s_{\mu}$) contributions.  In the case that a detection is made, we require that the observed brightness be greater than the brightness of the detection limit ($\fobs = f_i \ge b_i$) while in the case that no detection is made, we require that the brightness (if it could be measured) be less than the detection limit ($f_i < b_i$).  To derive the likelihood of the observed $\fobs$, given $\sigma_i$, $\theta$ and $I$, we must integrate over the prior distribution of the unknown $b_i$,
\begin{eqnarray}\displaystyle
p(\fobs |\sigma_i,\theta,I) &=& \left\{\begin{array}{ll}
  N(f_i | \mu_i,  \sigma_i^2 + s_{\mu}^2)\,  \int_0^{f_i} p(b_i | \theta)\, \dd b_i & \mbox{if $\fobs \ne \texttt{NA}$} \\
  \int_{0}^{\infty} \int_{0}^{b_i} N(f_i | \mu_i, \sigma_i^2 + s_{\mu}^2)\, p(b_i | \theta)\, \dd f_i\, \dd b_i & \mbox{if $\fobs = \texttt{NA}$} \\
\end{array}\right.\label{eq:mlik}
\\
p(b_i|\theta) &=& N(b_i|B,V_B)
\label{eq:bprior}
\\
\theta &\equiv& (\omega, \{A_k\}, \{\phi_k\}, s_\mu^2, B, V_B) \quad ,
\end{eqnarray}
where we have introduced the hyperparameters $B$ and $V_B$ for the Gaussian prior distribution of $b_i$.  In Equation \ref{eq:mlik}, in the epochs for which a detection was made ($\fobs \ne \texttt{NA}$), we marginalize over the unknown $b_i$ from $0$ (low brightness limit) to $f_i$, enforcing that the detection limit be fainter than the observed brightness.  Likewise, in the epochs for which no detection was made ($\fobs = \texttt{NA}$), we integrate the joint $(f_i, b_i)$ likelihood over all possible values of $b_i$ and over the unknown $f_i$ from $0$ to $b_i$, ensuring that the brightness (if it were able to be observed) be fainter than the detection limit.

In the above, we have assumed no extra information on each of the $b_i$ values besides the knowledge of whether a detection was made on that epoch.  Hence, we draw, in Equation \ref{eq:bprior}, each $b_i$ value from a global prior distribution which is the same at all epochs.  If instead, we are given an estimate of $b_i$ plus its error distribution for each epoch (which, in principle is estimable from the raw telescope images), we can replace Equation \ref{eq:bprior} by these epoch-wise distributions.  In the case that the $b_i$ are assumed to be completely known (without error), the data likelihood of $\fobs$ becomes
\begin{eqnarray}\displaystyle
p(\fobs |\sigma_i,\theta,I, b_i) &=& \left\{\begin{array}{ll}
  N(f_i | \mu_i,  \sigma_i^2 + s_{\mu}^2)\,  I(f_i \ge b_i) & \mbox{if $\fobs \ne \texttt{NA}$} \\
 \int_{0}^{b_i} N(f_i | \mu_i, \sigma_i^2 + s_{\mu}^2)\, \dd f_i & \mbox{if $\fobs = \texttt{NA}$} \\
\end{array}\right.\label{eq:mlik_s}
\end{eqnarray}
where the boolean indictor function, $I(f_i \ge b_i)$, is 1 if $f_i \ge b_i$ and 0 otherwise.

Next, we model the reported standard error, $\sobs$, on the uncertainty of the magnitude measurement.  Instead of assuming that $\sobs$ is a perfect, error-free measurement, we probabilistically connect it to the true uncertainty standard error, $\sigma_i$ through a truncated Gaussian likelihood, where the truncation enforces a non-negative variance for each observation.  Our likelihood of observed $\sobs$, given $\sigma_i$, $\theta$ and $I$, is
\begin{eqnarray}\displaystyle
p(\sobs | \sigma_i, \theta,I) &=& \left\{\begin{array}{ll}
  N(s_i|\sigma_i,v_\sigma) & \mbox{if $\sobs \ne \texttt{NA}$} \\
  \int_{0}^{\infty}  N(s_i | \sigma_i,v_\sigma)\,  \dd s_i & \mbox{if $\sobs = \texttt{NA}$}
\end{array}\right.\label{eq:slik}
\\
\theta &\equiv& (\omega, \{A_k\}, \{\phi_k\}, s_\mu^2, B, V_B ,v_\sigma) \quad ,
\end{eqnarray}
where we have added a model parameter $v_\sigma$, which represents the
variance in the distribution of reported uncertainties given the true
uncertainty.  The only purpose of
including the likelihood in Equation \ref{eq:slik} to the model, in practice, to keep the $\sigma_i$ from
drifting very far away from the $s_i$, as set by the hyperparameter
$v_\sigma$.

Putting it all together, we can write down the likelihood for the data, $D_i$, on a single epoch, as
\begin{eqnarray}\displaystyle
p(D_i|\theta,I) &=& \int_0^{\infty} p(\fobs |\sigma_i,\theta,I)\, p(\sobs |\sigma_i,\theta,I)\, p(\sigma_i | \theta)\,\dd \sigma_i
\\
p(\sigma_i|\theta) &\propto& \sigma_i^{-1}
\\
\theta &\equiv& (\omega, \{A_k\}, \{\phi_k\}, s_\mu^2, B, V_B ,v_\sigma) \quad ,
\end{eqnarray}
where we have inserted the expressions from Equations (\ref{eq:mlik}) and (\ref{eq:slik}), and integrated out the nuisance parameter, $\sigma_i$.  We have assumed a Jeffrey's prior on $\sigma_i$, which is non-informative and invariant to reparametrization of the variance.  We could alternatively use an inverse-gamma prior, which takes two hyperparameters (and is conjugate in the case of a normal likelihood with unknown variance).  We have also assumed that $\fobs$ and $\sobs$ are conditionally independent given $\sigma_i$, $\theta$, and $I$.  This is a reasonable assumption in the case that a detection is made at epoch $t_i$.

@@

>>>>

For each astronomical object, a photometric survey measures a multi-epoch light curve over $N$ (typically unevenly spaced) epochs.  At each epoch $i$, with associated time $t_i$, the survey takes an exposure at the location of the object and either (a) detects the object and records an estimate of its photon flux, $\fobs$ and the root variance of the statistical uncertainty in that estimate, $\sobs$, or (b) fails to detect the object.  In the latter case, most modern surveys either record a reference value to signify that no detection was made (as is done in ASAS) or an estimate of the upper detection limit, $b_i$, which is the brightest the object could have been given that it was not detected at a significant level by the software.

There are many reasons that a source might not show up in a catalog.  These include:
\begin{itemize}
\item low S/N of the source, due either to a higher noise level or a fainter signal,
\item the source falling outside of the detection window (e.g., near chip edge),
\item occulting of the source by an artifact of the detector (e.g., hot pixels, masked out), or
\item the source was out-shone by an intervening object (e.g., asteroid, comet, variable star, airplane, etc.).
\end{itemize}
Here, we present a statistical model that can be used to detect variable sources and model their variability using multi-epoch light curves containing epochs of non-detection.  Previous efforts to detect and model variability using multi-epoch photometry have typically ignored non-detections (REFs) or used them in an ad-hoc manner lacking statistical rigor (REFs).  An exception is \citet{2009AJ....137.4400L}, who measure proper motions of sources in SDSS falling below the detection limit.

In this paper, we will assume that $\fobs$ and $\sobs$ take on real-valued numbers in epochs for which the source was detected and receive the reference value {\tt NA} in epochs where no detection was made. For notational convenience we assemble all the light curve data for one source into a data set $D$ given by
\begin{eqnarray}\displaystyle
D &\equiv& \{D_i\}
\\
D_i &\equiv& (\fobs, \sobs)
\quad ,
\end{eqnarray}
where $(\fobs, \sobs)$ are the light curve measurements  at $t_i$.  The goal, for each astronomical object, is to construct the likelihood, $f^n$, for the data $D$, given a set of model parameters that describe the variability of the object and the characteristics of the observations, and either to maximize the likelihood with respect to the model parameters or to use it in further inference.

@@

To model the mean brightness of the light curve as a function of time, we use a multiple-harmonic Fourier model with angular oscillation frequency $\omega$,
\begin{eqnarray}\displaystyle
\mu_i &=& \sum_{k=1}^K A_k\, \sin (t_i \, \omega  k) + B_k\, \cos (t_i \, \omega  k)
\quad ,\label{eq:fourier}
\end{eqnarray}
where $\sqrt{A_k^2 + B_k^2}$ is the amplitude of the $k^{\rm th}$ harmonic of the frequency $\omega$ and $\tan^{-1}(B_k,A_k)$ is the relative phase offset of harmonic $k$.  In this analysis, we will fix the number of harmonics to $K=3$, though in principle we can use the data to choose the appropriate $K$ to capture the complexity of the light curve.  In addition to the expected brightness in Equation \ref{eq:fourier}, we assume that there is uncertainty or inappropriateness in the model, leading to a \emph{model variance} $s_\mu^2$ at each point (assumed constant but easily generalized).

Additionally, we need to instantiate a latent variable, $b_i$, to represent the detection limit, in units of flux, at epoch $i$.  The $b_i$ parameter is essential because it constrains the possible values of the mean brightness, $\mu_i$, of the light curve when there is a non-detection.  By employing a hierarchical model for the distribution of $b_i$, we can fully utilize all of the information encoded in both the detections and non-detections when computing the data likelihood.   At each epoch, we connect the observed flux, $\fobs$, to the latent variable, $f_i$, signifying the true observable flux of the object, via the detection limit, $b_i$ by
\begin{eqnarray}\displaystyle
\fobs &=& \left\{\begin{array}{ll}
  f_i & \mbox{if $f_i \ge b_i$} \\
  \texttt{NA} & \mbox{if $f_i < b_i$} \\
\end{array} \right.
\end{eqnarray}
so that the observed flux is \texttt{NA} only when the true observable flux, $f_i$, is below the detection limit, $b_i$.  And similarly, we introduce a latent variable, $s_i$, for the true observable standard error,
\begin{eqnarray}\displaystyle
\sobs &=& \left\{\begin{array}{ll}
  s_i & \mbox{if $f_i \ge b_i$} \\
  \texttt{NA} & \mbox{if $f_i < b_i$} \\
\end{array} \right.
\end{eqnarray}
so that the true observable standard error of the flux measurement is \texttt{NA} only when the true observable flux is below the detection limit.

@@

Hence, our initial model consists of the parameter vectors $\{f_1,...,f_N\}$, $\{s_1,...,s_N\}$, $\{b_1,...,b_N\}$ and $\{\sigma_1,...,\sigma_N\}$, and the model parameters
\begin{eqnarray}\displaystyle
\theta &\equiv& (\omega, \{A_k\}, \{B_k\}, s_\mu^2) \quad ,
\end{eqnarray}
along with prior information about observation times, $\{t_1,...,t_N\}$ and other prior assumptions, which we make explicit by creating the prior information set
\begin{eqnarray}\displaystyle
I &\equiv& (\{t_i\}, \mbox{assumptions}) \quad .
\end{eqnarray}
Our goal is to write down the form of the likelihood of the data, $D$, given $\theta$ and $I$.  Then, for each light curve we can find the vector $\theta$ that maximizes the data likelihood.

@@

We model the observed flux, $\fobs$, as a Gaussian distribution with variance that has both measurement ($\sigma_i$) and model ($s_{\mu}$) contributions.  In the case that a detection is made, we require that the observed brightness be greater than the brightness of the detection limit ($\fobs = f_i \ge b_i$) while in the case that no detection is made, we require that the brightness (if it could be measured) be less than the detection limit ($f_i < b_i$).  To derive the likelihood of the observed $\fobs$, given $\sigma_i$, $\theta$ and $I$, we must integrate over the prior distribution of the unknown $b_i$,
\begin{eqnarray}\displaystyle
p(\fobs |\sigma_i,\theta,I) &=& \left\{\begin{array}{ll}
  N(f_i | \mu_i,  \sigma_i^2 + s_{\mu}^2)\,  \int_0^{f_i} p(b_i | \theta)\, \dd b_i & \mbox{if $\fobs \ne \texttt{NA}$} \\
  \int_{0}^{\infty} \int_{0}^{b_i} N(f_i | \mu_i, \sigma_i^2 + s_{\mu}^2)\, p(b_i | \theta)\, \dd f_i\, \dd b_i & \mbox{if $\fobs = \texttt{NA}$} \\
\end{array}\right.\label{eq:mlik}
\\
p(b_i|\theta) &=& N(b_i|B,V_B)
\label{eq:bprior}
\\
\theta &\equiv& (\omega, \{A_k\}, \{B_k\}, s_\mu^2, B, V_B) \quad ,
\end{eqnarray}
where we have introduced the hyperparameters $B$ and $V_B$ for the Gaussian prior distribution of $b_i$.  In Equation \ref{eq:mlik}, in the epochs for which a detection was made ($\fobs \ne \texttt{NA}$), we marginalize over the unknown $b_i$ from $0$ (low brightness limit) to $f_i$, enforcing that the detection limit be fainter than the observed brightness.  Likewise, in the epochs for which no detection was made ($\fobs = \texttt{NA}$), we integrate the joint $(f_i, b_i)$ likelihood over all possible values of $b_i$ and over the unknown $f_i$ from $0$ to $b_i$, ensuring that the brightness (if it were able to be observed) be fainter than the detection limit.

In the above, we have assumed no extra information on each of the $b_i$ values besides the knowledge of whether a detection was made on that epoch.  Hence, we draw, in Equation \ref{eq:bprior}, each $b_i$ value from a global prior distribution which is the same at all epochs.  If instead, we are given an estimate of $b_i$ plus its error distribution for each epoch (which, in principle can be inferred from the raw telescope images), we can replace Equation \ref{eq:bprior} with a different distribution per epoch.  In the case that the $b_i$ are assumed to be completely known (without error), the data likelihood of $\fobs$ becomes
\begin{eqnarray}\displaystyle
p(\fobs |\sigma_i,\theta,I, b_i) &=& \left\{\begin{array}{ll}
  N(f_i | \mu_i,  \sigma_i^2 + s_{\mu}^2)\,  I(f_i \ge b_i) & \mbox{if $\fobs \ne \texttt{NA}$} \\
 \int_{0}^{b_i} N(f_i | \mu_i, \sigma_i^2 + s_{\mu}^2)\, \dd f_i & \mbox{if $\fobs = \texttt{NA}$} \\
\end{array}\right.\label{eq:mlik_s}
\end{eqnarray}
where the boolean indictor function, $I(f_i \ge b_i)$, is 1 if $f_i \ge b_i$ and 0 otherwise.

Next, we model the reported standard error, $\sobs$, on the uncertainty of the magnitude measurement.  Instead of assuming that $\sobs$ is a perfect, error-free measurement, we probabilistically connect it to the true uncertainty standard error, $\sigma_i$ through a truncated Gaussian likelihood, where the truncation enforces a non-negative variance for each observation.  Our likelihood of observed $\sobs$, given $\sigma_i$, $\theta$ and $I$, is
\begin{eqnarray}\displaystyle
p(\sobs | \sigma_i, \theta,I) &=& \left\{\begin{array}{ll}
  N(s_i|\sigma_i,v_\sigma) & \mbox{if $\sobs \ne \texttt{NA}$} \\
  \int_{0}^{\infty}  N(s_i | \sigma_i,v_\sigma)\,  \dd s_i & \mbox{if $\sobs = \texttt{NA}$}
\end{array}\right.\label{eq:slik}
\\
\theta &\equiv& (\omega, \{A_k\}, \{B_k\}, s_\mu^2, B, V_B ,v_\sigma) \quad ,
\end{eqnarray}
\joey{Need a distribution that is truncated at 0. Something better? }
where we have added a model parameter $v_\sigma$, which represents the
variance in the distribution of reported uncertainties given the true
uncertainty.  The only purpose of 
 including the likelihood in Equation \ref{eq:slik} to the model, in practice, to keep the $\sigma_i$ from
drifting very far away from the $s_i$, as set by the hyperparameter
$v_\sigma$.

Putting it all together, we can write down the likelihood of the data, $D_i$, for the parameters $\theta$, on a single epoch, as
\begin{eqnarray}\displaystyle
p(D_i|\theta,I) &=& \int_0^{\infty} p(\fobs |\sigma_i,\theta,I)\, p(\sobs |\sigma_i,\theta,I)\, p(\sigma_i | \theta)\,\dd \sigma_i
\\
p(\sigma_i|\theta) &\propto& \sigma_i^{-1}
\\
\theta &\equiv& (\omega, \{A_k\}, \{B_k\}, s_\mu^2, B, V_B ,v_\sigma) \quad ,
\end{eqnarray}
where we have inserted the expressions from Equations (\ref{eq:mlik}) and (\ref{eq:slik}), and integrated out the nuisance parameter, $\sigma_i$.  We have assumed a Jeffrey's prior on $\sigma_i$, which is non-informative and invariant to reparametrization of the variance.  We could alternatively use an inverse-gamma prior, which takes two hyperparameters (and is conjugate in the case of a normal likelihood with unknown variance).  We have also assumed that $\fobs$ and $\sobs$ are conditionally independent given $\sigma_i$, $\theta$, and $I$.  This is a reasonable assumption in the case that a detection is made at epoch $t_i$.

@@

\subsection{Mixture Model for $\fobs$ or $\sobs$}

This may be too much for this paper, but will be useful in the presence of crappy data.
